Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-04-05 thirdPaper/draft/typeConeAssociahedra.tex
AR quivers non-kissing

\usepackage[T1]{fontenc}
\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray, overpic, nicefrac}
\usepackage[noabbrev,capitalise]{cleveref}
\usepackage[normalem]{ulem}
\usepackage{marginnote}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue}
\usepackage[all]{xy}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{tkz-graph}
\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
\graphicspath{{figures/}{figures/walks/}{figures/tubes/}}
\makeatletter\def\input@path{{figures/}}\makeatother
\usepackage{caption}
\captionsetup{width=\textwidth}

@@

@@

\begin{figure}[h]
	\capstart
	%\centerline{\includegraphics[scale=.45]{clusterFans}}
	\centerline{
	\begin{overpic}[scale=.45]{clusterFans}
	\put(-19,30){$\left[\begin{array}{@{}c@{\;}c@{\;}c@{}} 0 & -1 & 1 \\ 1 & 0 & -1 \\ -1 & 1 & 0 \end{array}\right]$}
	\put(98,30){$\left[\begin{array}{@{}c@{\;}c@{\;}c@{}} 0 & -1 & 2 \\ 1 & 0 & -2 \\ -1 & 1 & 0 \end{array}\right]$}
	\end{overpic}
	}
	\caption{Two cluster fans~$\gvectorFan[\B_\circ]$ for the type~$A_3$~(left) and type~$C_3$~(right) cyclic initial exchange matrices. As the fans are $3$-dimensional, we intersect them with the sphere and stereographically project them from the direction~$(-1,-1,-1)$. Illustration from~\cite{HohlwegPilaudStella}.}
	\label{fig:clusterFans}
\end{figure}

\begin{theorem}
\label{thm:gvectorFanCA}
For any finite type exchange matrix~$\B_\circ$, the collection of cones \\[.1cm]
\centerline{
$\gvectorFan[\B_\circ] \eqdef \bigset{\R_{\ge0} \, \gvectorsFull{\B_\circ}{\seed}}{\seed \text{ seed of } \principalClusterAlgebra},$
} \\[.1cm]
together with all their faces, forms a complete simplicial fan, called the \defn{$\b{g}$-vector fan} or \defn{cluster fan} of~$\B_\circ$.
\end{theorem}

@@

\[
\begin{array}{r|ccccccccc}
\text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1 + x_2}{x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} \\[.2cm]
\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{1}{-1} & \compactVector{0}{0}{-1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} \\[.6cm]
\text{linearity}	& 0 & 0 & 1 & 1 & 0 & -1 & -1 & 0 & 0 \\
\text{space}		& 0 & -1 & 0 & 0 & 1 & -1 & 0 & 0 & 1 \\
					& 1 & 1 & 0 & -1 & 0 & 1 & 0 & -1 & -1 \\[.2cm]
\text{inequalities} & -1 & 0 & 0 & 0 & 1 & 1 & -1 & 0 & 0 \\
 					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 \\
 					& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 \\
 					& 0 & 0 & 1 & -1 & 0 & 0 & 0 & 1 & 0 \\
 					& 0 & 1 & 0 & 0 & 0 & -1 & 1 & 0 & 0 \\
 					& 0 & -1 & 0 & 1 & 0 & 1 & 0 & -1 & 0 \\[.2cm]
\end{array}
\]

@@

\[
\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;}c@{}c@{}c@{}c}
\text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2}{x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_2 x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_1 x_3 + x_3^2}{x_2^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_2 x_3 + x_3^2}{x_1^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3 + x_2 x_3}{x_1 x_2 x_3}$} \\[.2cm]
\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{2}{-1} & \compactVector{0}{1}{-1} & \compactVector{-1}{1}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} & \compactVector{-2}{0}{1} & \compactVector{-1}{0}{0}  \\[.6cm]
\text{linearity}	& 1 & 1 & 2 & 1 & 0 & 0 & -1 & 0 & -1 & -2 & 0 & -1 \\
\text{space}		& 0 & 1 & 0 & 0 & -1 & 2 & 1 & 1 & -1 & 0 & 0 & 0 \\
					& 0 & 0 & -1 & -1 & 0 & 1 & 1 & 0 & 0 & 1 & -1 & 0 \\[.2cm]
\text{inequalities} & 0 & 0 & 0 & 0 & 0 & 1 & 0 & -2 & 0 & 0 & 1 & 0 \\
					& 0 & 1 & 0 & 0 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 \\
					& 0 & -1 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & 0 & -1 & 0 \\
					& -1 & 0 & 0 & 0 & 1 & 0 & 1 & 0 & 0 & -1 & 0 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 \\
					& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & 1 & -2 & 0 & 0 & 1 & 0 & 0 \\
					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 & 0 & 0 \\
					& 0 & 0 & 1 & -2 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 \\[.2cm]
\end{array}
\]

@@

\[
\begin{array}{r|cccccccc}
\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA8}} \\[.6cm]
\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
\text{linearity}	& 0 & -1 & 0 & 1 & -1 & 0 & 1 & 0 \\
\text{space}		& 1 & 1 & 0 & 0 & 1 & -1 & -1 & 0 \\
					& 0 & 0 & 1 & 0 & -1 & 0 & 0 & -1 \\[.2cm]
\text{inequalities} & -1 & 0 & 0 & 1 & 1 & 0 & 0 & -1 \\
					& 1 & 0 & 0 & -1 & 0 & 0 & 1 & 0 \\
					& 0 & -1 & 1 & 0 & 1 & 0 & 0 & 0 \\
					& 0 & 0 & 0 & 1 & 0 & 1 & -1 & 0 \\
					& 0 & 1 & 0 & 0 & -1 & 0 & 0 & 1 \\[.2cm]
\end{array}
\]

@@

\[
\begin{array}{r|c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c}
\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB11}} \\[.6cm]
\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{1}{0}{-1} & \compactVector{0}{-1}{1} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
\text{linearity}	& 0 & -1 & 0 & 1 & 0 & 1 & -1 & 0 & 0 & 1 & 0 \\
\text{space}		& 1 & 0 & 0 & 1 & 1 & 0 & 0 & -1 & -1 & 0 & 0 \\
					& 1 & 0 & 1 & 1 & 0 & 1 & -1 & 0 & -1 & 0 & -1 \\[.2cm]
\text{inequalities} & 0 & 0 & 0 & 1 & 0 & -1 & 0 & 1 & 0 & 0 & 0 \\
					& -1 & 1 & 0 & 0 & 1 & 0 & -1 & 0 & 0 & 0 & 0 \\
					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 0 & 0 & 1 \\
					& 1 & 0 & -1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
					& 0 & 0 & 0 & 1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 \\
					& 0 & 0 & 1 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -1 & 1 & -1 & 0 \\
					& 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 & 0 & 1 & -1 \\
					& 0 & -1 & 0 & 0 & 0 & 0 & 1 & 1 & -1 & 0 & 0 \\[.2cm]
\end{array}
\]

%sage: Q = GentleQuiver({'e1':{'e2':['a']}, 'e2':{'e3':['b']}, 'e3':{'e1':['c']}}, [('b','c')])
%
%sage: Q.non_kissing_fan().rays()
%N( 1,  0,  0),0
%N( 0,  0,  1),1
%N( 1,  0, -1),2
%N( 1, -1,  0),3
%N( 0,  0, -1),4
%N(-1,  0,  1),5
%N( 0, -1,  0),6
%N( 0, -1,  1),7
%N(-1,  0,  0),8
%N( 0,  1,  0),9
%N( 0,  1, -1)10
%in 3-d lattice N
%
%sage: TCNKC = type_cone_NKC(Q)
%sage: TCNKC
%A 11-dimensional polyhedron in QQ^11 defined as the convex hull of 1 vertex, 9 rays, 3 lines
%sage: TCNKC.lines()
%(A line in the direction (0, 0, 0, 1, 0, 0, 1, 1, 0, -1, -1),
% A line in the direction (1, 0, 1, 1, 0, -1, 0, 0, -1, 0, 0),
% A line in the direction (1, 1, 0, 1, -1, 0, 0, 1, -1, 0, -1))
%sage: TCNKC.inequalities()
%(An inequality (0, 0, 0, 1, 0, 1, 0, -1, 0, 0, 0) x + 0 >= 0,
% An inequality (-1, 0, 1, 0, 0, 0, 0, 0, 0, 1, -1) x + 0 >= 0,
% An inequality (1, 0, -1, 0, 1, 0, 0, 0, 0, 0, 0) x + 0 >= 0,
% An inequality (1, -1, 0, -1, 0, 0, 0, 1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 1) x + 0 >= 0,
% An inequality (0, 1, 0, 0, 0, 0, 1, -1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 0, 0, 0, -1, -1, 1, 1, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 1, -1, -1, 0, 1, 0, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 0, 0, 0, 1, 0, 0, -1, -1, 1) x + 0 >= 0)
%sage: TCNKC.lines()
%(A line in the direction (0, 0, 0, 1, 0, 0, 1, 1, 0, -1, -1),
% A line in the direction (1, 0, 1, 1, 0, -1, 0, 0, -1, 0, 0),
% A line in the direction (1, 1, 0, 1, -1, 0, 0, 1, -1, 0, -1))
\vincent{Todo}
\vincent{Pictures AR quivers + labeling of meshes reported on the inequalities.}
\end{example}

>>>>

\usepackage[T1]{fontenc}
\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray, overpic, nicefrac}
\usepackage[noabbrev,capitalise]{cleveref}
\usepackage[normalem]{ulem}
\usepackage{marginnote}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue}
\usepackage[all]{xy}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{tkz-graph}
\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
\graphicspath{{figures/}{figures/walks/}{figures/tubes/}}
\makeatletter\def\input@path{{figures/}}\makeatother
\usepackage{caption}
\captionsetup{width=\textwidth}
\usepackage[export]{adjustbox}

@@

\vincent{Example type cone}

@@

\begin{figure}[h]
	\capstart
	%\centerline{\includegraphics[scale=.45]{clusterFans}}
	\begin{adjustbox}{center}
    	\begin{overpic}[scale=.45]{clusterFans}
    	\put(-19,30){$\left[\begin{array}{@{}c@{\;}c@{\;}c@{}} 0 & -1 & 1 \\ 1 & 0 & -1 \\ -1 & 1 & 0 \end{array}\right]$}
    	\put(98,30){$\left[\begin{array}{@{}c@{\;}c@{\;}c@{}} 0 & -1 & 2 \\ 1 & 0 & -2 \\ -1 & 1 & 0 \end{array}\right]$}
    	\end{overpic}
	\end{adjustbox}
	\caption{Two cluster fans~$\gvectorFan[\B_\circ]$ for the type~$A_3$~(left) and type~$C_3$~(right) cyclic initial exchange matrices. As the fans are $3$-dimensional, we intersect them with the sphere and stereographically project them from the direction~$(-1,-1,-1)$. Illustration from~\cite{HohlwegPilaudStella}.}
	\label{fig:clusterFans}
\end{figure}

\begin{theorem}
\label{thm:gvectorFanCA}
For any finite type exchange matrix~$\B_\circ$, the collection of cones
\[
\gvectorFan[\B_\circ] \eqdef \bigset{\R_{\ge0} \, \gvectorsFull{\B_\circ}{\seed}}{\seed \text{ seed of } \principalClusterAlgebra},
\]
together with all their faces, forms a complete simplicial fan, called the \defn{$\b{g}$-vector fan} or \defn{cluster fan} of~$\B_\circ$.
\end{theorem}

@@

\[
\begin{array}{r|ccccccccc}
\text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1 + x_2}{x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} \\[.2cm]
\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{1}{-1} & \compactVector{0}{0}{-1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} \\[.6cm]
%\text{linearity}	& 0 & 0 & 1 & 1 & 0 & -1 & -1 & 0 & 0 \\
%\text{space}		& 0 & -1 & 0 & 0 & 1 & -1 & 0 & 0 & 1 \\
%					& 1 & 1 & 0 & -1 & 0 & 1 & 0 & -1 & -1 \\[.2cm]
\text{facet}		& -1 & 0 & 0 & 0 & 1 & 1 & -1 & 0 & 0 \\
\text{defining} 	& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 \\
\text{inequalities}	& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 \\
 					& 0 & 0 & 1 & -1 & 0 & 0 & 0 & 1 & 0 \\
 					& 0 & 1 & 0 & 0 & 0 & -1 & 1 & 0 & 0 \\
 					& 0 & -1 & 0 & 1 & 0 & 1 & 0 & -1 & 0 \\[.2cm]
\end{array}
\]

@@

\[
\begin{array}{r|c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;\;}c@{\;}c@{\;}c@{\;}c@{}c@{}c@{}c}
\text{variables} & \rotatebox{70}{$x_1$} & \rotatebox{70}{$x_2$} & \rotatebox{70}{$x_3$} & \rotatebox{70}{$\frac{x_2 + x_3}{x_1}$} & \rotatebox{70}{$\frac{x_1 + x_3}{x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2}{x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3}{x_2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_2 x_3}{x_1 x_3}$} & \rotatebox{70}{$\frac{x_1 + x_2 + x_3}{x_1 x_2}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_1 x_3 + x_3^2}{x_2^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + 2 x_2 x_3 + x_3^2}{x_1^2 x_3}$} & \rotatebox{70}{$\frac{x_1^2 + x_2^2 + x_1 x_3 + x_2 x_3}{x_1 x_2 x_3}$} \\[.2cm]
\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{-1}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{2}{-1} & \compactVector{0}{1}{-1} & \compactVector{-1}{1}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} & \compactVector{-2}{0}{1} & \compactVector{-1}{0}{0}  \\[.6cm]
%\text{linearity}	& 1 & 1 & 2 & 1 & 0 & 0 & -1 & 0 & -1 & -2 & 0 & -1 \\
%\text{space}		& 0 & 1 & 0 & 0 & -1 & 2 & 1 & 1 & -1 & 0 & 0 & 0 \\
%					& 0 & 0 & -1 & -1 & 0 & 1 & 1 & 0 & 0 & 1 & -1 & 0 \\[.2cm]
\text{facet}		& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -2 & 0 & 0 & 1 & 0 \\
\text{defining}		& 0 & 1 & 0 & 0 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 \\
\text{inequalities}	& 0 & -1 & 0 & 1 & 0 & 0 & 0 & 1 & 0 & 0 & -1 & 0 \\
					& -1 & 0 & 0 & 0 & 1 & 0 & 1 & 0 & 0 & -1 & 0 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 \\
					& 0 & 0 & -1 & 1 & 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 \\
					& 0 & 0 & 0 & 0 & 0 & 1 & -2 & 0 & 0 & 1 & 0 & 0 \\
					& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 & 0 & 0 \\
					& 0 & 0 & 1 & -2 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 \\[.2cm]
\end{array}
\]

@@

\[
\begin{array}{r|ccccccccc}
\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkA8}} \\[.6cm]
\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
%\text{linearity}	& 0 & -1 & 0 & 1 & -1 & 0 & 1 & 0 \\
%\text{space}		& 1 & 1 & 0 & 0 & 1 & -1 & -1 & 0 \\
%					& 0 & 0 & 1 & 0 & -1 & 0 & 0 & -1 \\[.2cm]
\text{facet}		& 0 & -1 & 1 & 0 & 1 & 0 & 0 & 0 & \red \circled{A} \\
\text{defining}		& 0 & 1 & 0 & 0 & -1 & 0 & 0 & 1 & \red \circled{B} \\
\text{inequalities}	& -1 & 0 & 0 & 1 & 1 & 0 & 0 & -1 & \red \circled{C} \\
					& 1 & 0 & 0 & -1 & 0 & 0 & 1 & 0 & \red \circled{D} \\
					& 0 & 0 & 0 & 1 & 0 & 1 & -1 & 0 & \red \circled{E} \\[.2cm]
\end{array}
\]

@@

\[
\begin{array}{r|c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}c@{\;}cc}
\text{walks} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB1}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB2}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB3}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB4}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB5}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB6}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB7}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB8}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB9}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB10}} & \raisebox{-.4cm}{\includegraphics[scale=.5]{walkB11}} \\[.6cm]
\text{$\b{g}$-vectors} & \compactVector{1}{0}{0} & \compactVector{0}{1}{0} & \compactVector{0}{0}{1} & \compactVector{1}{-1}{0} & \compactVector{1}{0}{-1} & \compactVector{0}{-1}{1} & \compactVector{0}{1}{-1} & \compactVector{-1}{0}{1} & \compactVector{-1}{0}{0} & \compactVector{0}{-1}{0} & \compactVector{0}{0}{-1} \\[.6cm]
%\text{linearity}	& 0 & -1 & 0 & 1 & 0 & 1 & -1 & 0 & 0 & 1 & 0 \\
%\text{space}		& 1 & 0 & 0 & 1 & 1 & 0 & 0 & -1 & -1 & 0 & 0 \\
%					& 1 & 0 & 1 & 1 & 0 & 1 & -1 & 0 & -1 & 0 & -1 \\[.2cm]
\text{facet}		& -1 & 1 & 0 & 0 & 1 & 0 & -1 & 0 & 0 & 0 & 0 & \red \circled{A} \\
\text{defining}		& 1 & 0 & 0 & 0 & -1 & 0 & 0 & 0 & 0 & 0 & 1 & \red \circled{B} \\
\text{inequalities}	& 0 & 0 & 0 & 1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 & \red \circled{C} \\
					& 1 & 0 & -1 & -1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & \red \circled{D} \\
					& 0 & 0 & 0 & -1 & 1 & 0 & 0 & 0 & 0 & 1 & -1 & \red \circled{E} \\
					& 0 & 0 & 1 & 0 & 0 & -1 & 0 & 0 & 0 & 1 & 0 & \red \circled{F}\\
					& 0 & 0 & 0 & 1 & 0 & -1 & 0 & 1 & 0 & 0 & 0 & \red \circled{G} \\
					& 0 & 0 & 0 & 0 & 0 & 1 & 0 & -1 & 1 & -1 & 0 & \red \circled{H} \\
					& 0 & -1 & 0 & 0 & 0 & 0 & 1 & 1 & -1 & 0 & 0 & \red \circled{K} \\[.2cm]
\end{array}
\]

%sage: Q = GentleQuiver({'e1':{'e2':['a']}, 'e2':{'e3':['b']}, 'e3':{'e1':['c']}}, [('b','c')])
%
%sage: Q.non_kissing_fan().rays()
%N( 1,  0,  0),0
%N( 0,  0,  1),1
%N( 1,  0, -1),2
%N( 1, -1,  0),3
%N( 0,  0, -1),4
%N(-1,  0,  1),5
%N( 0, -1,  0),6
%N( 0, -1,  1),7
%N(-1,  0,  0),8
%N( 0,  1,  0),9
%N( 0,  1, -1)10
%in 3-d lattice N
%
%sage: TCNKC = type_cone_NKC(Q)
%sage: TCNKC
%A 11-dimensional polyhedron in QQ^11 defined as the convex hull of 1 vertex, 9 rays, 3 lines
%sage: TCNKC.lines()
%(A line in the direction (0, 0, 0, 1, 0, 0, 1, 1, 0, -1, -1),
% A line in the direction (1, 0, 1, 1, 0, -1, 0, 0, -1, 0, 0),
% A line in the direction (1, 1, 0, 1, -1, 0, 0, 1, -1, 0, -1))
%sage: TCNKC.inequalities()
%(An inequality (0, 0, 0, 1, 0, 1, 0, -1, 0, 0, 0) x + 0 >= 0,
% An inequality (-1, 0, 1, 0, 0, 0, 0, 0, 0, 1, -1) x + 0 >= 0,
% An inequality (1, 0, -1, 0, 1, 0, 0, 0, 0, 0, 0) x + 0 >= 0,
% An inequality (1, -1, 0, -1, 0, 0, 0, 1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, -1, 1, 0, 0, 0, 0, 0, 0, 1) x + 0 >= 0,
% An inequality (0, 1, 0, 0, 0, 0, 1, -1, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 0, 0, 0, -1, -1, 1, 1, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 1, -1, -1, 0, 1, 0, 0, 0, 0) x + 0 >= 0,
% An inequality (0, 0, 0, 0, 0, 1, 0, 0, -1, -1, 1) x + 0 >= 0)
%sage: TCNKC.lines()
%(A line in the direction (0, 0, 0, 1, 0, 0, 1, 1, 0, -1, -1),
% A line in the direction (1, 0, 1, 1, 0, -1, 0, 0, -1, 0, 0),
% A line in the direction (1, 1, 0, 1, -1, 0, 0, 1, -1, 0, -1))
